%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Experience}
{Experience}
{PDF:Experience}

\Entry
\href{http://taxibeat.gr}
{\textbf{BEAT}}, Athens

\Gap
\BulletItem
Big Data Software Engineer
\hfill
\DatestampYMD{2017}{8}{31} --
Present
\begin{Detail}
	\SubBulletItem
	Developing software for large scale data processing.
	\SubBulletItem
	Tools: Scala, Spark, Hadoop, MySQL
	
	
\end{Detail}

\Entry
\href{http://cslab.ece.ntua.gr}
{\textbf{Computing Systems Laboratory (CSLab)}},
NTUA, Greece

\Gap
\BulletItem
Researcher
\hfill
\DatestampYMD{2015}{8}{1} --
\DatestampYMD{2017}{8}{31}
\begin{Detail}
	\SubBulletItem
	Research and development on Big Data Management, Databases and\\ MultiEngine
	Analytics. Participated in four publications.
	\SubBulletItem
	I developed a middleware optimization framework for Spark SQL, achieving
	execution\\ time improvement for queries over heterogeneous environments up to one order of magnitude.
	\SubBulletItem
	Participated in the EU Funded Project ASAP(A Scalable AnalyticsPlatform).
	\SubBulletItem
	Paper review.
\end{Detail}

\Entry
\href{http://ismood.gr}
{\textbf{isMOOD Data Technology Services}}

\Gap
\BulletItem
Software Engineer
\hfill
\DatestampYMD{2014}{4}{1} --
\DatestampYMD{2015}{8}{31}
\begin{Detail}
	\SubBulletItem
	Data collection and integration into a unified source
	\SubBulletItem
	Development, scheduling \& optimization of web crawlers/spiders
	\SubBulletItem
	Tools: Scrapy, Python, Elasticsearch, MongoDB
\end{Detail}

\Entry
\href{http://microsoft.gr}
{\textbf{Microsoft Hellas}}

\Gap
\BulletItem
Student Partner
\hfill
\DatestampYMD{2013}{9}{1} --
\DatestampYMD{2014}{9}{1}
\begin{Detail}
	\SubBulletItem
	Presentations at Ionian University about Microsoft .NET technologies.
	\SubBulletItem
	I developed 2 Windows Phone and 2 Windows 8 applications.
\end{Detail}